MCTS Applied to Co-operative Problems

### 2015-08-01 Report/response.tex

We have changed the description of \emph{Doors} to better reflect what they look like when open.

We have added a definition for the \emph{Floor}.

We have improved the definition for \emph{Door} in order to make it clearer that the \emph{Door} closes again when the \emph{Buttons} are no longer activated.

We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
\subsection{Review 2 (Reviewer )}
\subsection{Review 3 (Reviewer G)}
We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.

We have corrected the typo in the definition of \emph{Walls} in the problem domain section.

The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
\subsection{Review 4 (Reviewer )}
\subsection{Review 5 (Reviewer )}
\end{document}

### 2015-08-01 Report/ceec.tex
Added section on the action cycle

>>>>

Each \emph{Agent} is able to make a single action in each game tick. The actions are polled from each \emph{Agent} that is given the state of the game. When every \emph{Agent} has returned an action, the game is updated with these actions. The actions are implemented sequentially, if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}. The available 5 actions are:
\begin{itemize}
\item{\emph{Left} - This will move the \emph{Agent} one grid square to the left. (-1, 0)}
\item{\emph{Right} - This will move the \emph{Agent} one grid square to the right. (1, 0)}
\item{\emph{Up} - This will move the \emph{Agent} one grid square up. (0, -1)}
\item{\emph{Down} - This will move the \emph{Agent} one grid square down. (0, 1)}
\item{\emph{No-Op} - This will not move the \emph{Agent}. It will remain in the same location as the previous game state.}
\end{itemize}
